Risk Factors and Treatment of Refractory Anaphylaxis - a systematic review

### 2017-12-07 analysis/paper/paper.Rmd
Biomarkers

---
title: 'Risk Factors and Treatment of Refractory Anaphylaxis - a systematic review'
author:
  - Wojciech Francuzik
  - Sabine Dölle
  - Margitta Worm, MD
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::word_document2:
    fig_caption: yes
    reference_docx: "../templates/template.docx"
bibliography: references.bib
csl: mee.csl
abstract: |
  **Introduction:**  Refractory anaphylaxis cases do not respond to treatment with intramuscular adrenaline. The incidence of refractory anaphylaxis is estimated to range between 3--5% of all cases of anaphylaxis. The risk factors for refractory anaphylaxis are unknown. In the present analysis, we aimed to evaluate the management and risk factors of refractory anaphylaxis to highlight possible clinical implications for updating current management algorithms.

@@

In clinical practice, it is necessary to identify patients at risk. Such risk factors should particularly be assessed in patients undergoing medical diagnostic and therapeutic measures. The measurement of tryptase enables to identify patients who are at risk for severe anaphylaxis.

For the future, biomarker measurements at a bedside setting may enable doctors to identify patients experiencing severe, refractory anaphylaxis early in order to initiate intensified critical care treatment. Moreover, defined standardized treatment protocols for such cases of refractory anaphylaxis may provide an optimization of the treatment which can save the life in a given patient.

>>>>

---
title: 'Risk Factors and Treatment of Refractory Anaphylaxis - a systematic review'
author:
  - Wojciech Francuzik
  - Sabine Dölle
  - Margitta Worm, MD
date: "`r format(Sys.time(), '%d.%m.%Y')`"
output: 
  bookdown::word_document2:
    fig_caption: yes
    reference_docx: "../templates/template.docx"
bibliography: references.bib
csl: mee.csl
abstract: |
  **Introduction:**  Refractory anaphylaxis cases do not respond to treatment with intramuscular adrenaline. The incidence of refractory anaphylaxis is estimated to range between 3--5% of all cases of anaphylaxis. The risk factors for refractory anaphylaxis are unknown. In the present analysis, we aimed to evaluate the management and risk factors of refractory anaphylaxis to highlight possible clinical implications for updating current management algorithms.

@@

In clinical practice, it is necessary to identify patients at risk. Such risk factors should particularly be assessed in patients undergoing medical diagnostic and therapeutic measures. The diagnosis of anaphylaxis is based on unspecific clinical presentation, most frequently with hypotension, bronchospasm and skin flushing. In cases where anaphylaxis is possible but the symptoms are not clearly apparent introduction of a point-of-case test could confirm the suspition in order to introduce immediate therapy with adrenaline. The measurement of tryptase enables to identify patients who are at risk for severe anaphylaxis (specificity of 0.93) but its sensitivity of 0.36 is insufficient [@Brown2004].

For the future,  measurements [@Wittenberg2017] at a bedside setting may enable doctors to identify patients experiencing severe, refractory anaphylaxis early in order to initiate intensified critical care treatment. Moreover, defined standardized treatment protocols for such cases of refractory anaphylaxis may provide an optimization of the treatment which can save the life in a given patient.
